\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-10-29 src/chain.tex
ft introduction

\section{Fault Tolerance}

>>>>

\section{Fault Tolerance}
In this section we consider the problem of a service chain placement when there 
is also demand for fault tolerance.
Formally, given a physical network, a virtual specification and a parameter 
$\phi \in \mathbb{N}$, a $\phi$-robust placement is a collection of $\phi$ placements,
$f_1,\ldots,f_\phi$,
that correspond to $\phi$ internal vertex disjoint physical paths. 
We are looking for a $\phi$-robust placement that minimize the total cost:
$$
\sum_{i = 1}^\phi \sum_j c(\alpha_j,f_i(\alpha_j))
$$
